# Test Zeroshot Classification based on "Digitalty" definition against human coded sample:

### Label to identiy:
The text is a statement that relates to the digital sphere in the widest sense. This may include general or specific themes related to the internet, digital communications and services, algorithms and digitized data, or the technologies that underpin digitalisation.'"


```{r}
outfile <- "zs_subtopics.csv"
googledrive::drive_download(paste0("TRIAS/", outfile), paste0("data/", outfile), overwrite = T)
zeroshot_unfiltered <-  
    read_csv(paste0("data/", outfile)) %>% 
  # if any coder identified digitality, we treat paragraph as digital:
  mutate(target = target_max) %>% 
  arrange(id, coder_ID) 

zeroshot <- zeroshot_unfiltered %>%
  filter(coder_ID != 666) # Cases qualitatively filtered out before human coding
```


```{r}
# define cutoff function ####

calc_cutoff_candidates <- function(cutoffvar, targetvar, seqstart = 0, seqend = 1, seqstep = .01, facetingvar = "cutoff") {
  ### targetvar: boolean!
  ### facetingvar needs to be present in  long format data!
  
  library(magrittr)
  
  inputdata <- tibble(
    targetvar = targetvar,
    cutoffvar = cutoffvar,
    facetingvar = facetingvar
  )
  df <- inputdata
  
  cutoff_candidates <- tibble()
  facets <- unique(facetingvar)
    
  for (facet in facets) {
      
      df <- filter(inputdata, facetingvar == facet)
      
      for (cutoff in seq(seqstart, seqend, seqstep)) {
      
        df %<>% mutate(pred = cutoffvar > cutoff) 
        
        TP <- sum(df$pred & df$targetvar)
        TN <- sum(!df$pred & !df$targetvar)
        FP <- sum(df$pred & !df$targetvar)
        FN <- sum(!df$pred & df$targetvar)
        
        precision <- TP / (TP + FP)
        recall <- TP / (TP + FN)
        f1 <- 2*(precision*recall)/(precision+recall)
        accuracy <- (TP + TN) / (TP + TN + FP + FN)
        baccuracy <- ((TP / (TP + FN)) + (TN / (TN + FP))) / 2 # Balanced accuracy (because imbalanced sample!) - https://neptune.ai/blog/balanced-accuracy
        
        cutoff_candidates %<>% 
          bind_rows(., tibble_row(cutoff, precision, recall, f1, accuracy, baccuracy, TP, FP, TN, FN, facet))
      }
  }
  return(cutoff_candidates)
}


# define plotting function ####

plot_metrics <- function(data, scorename, plotname, facetingvar = NULL){

  library(magrittr)
  data %<>% mutate(facet = facetingvar)
  
  best_candidate <- data
    
   if (!is.null(facetingvar)) {best_candidate %<>% filter(facet == "max_subtopic")}
     
  best_candidate <- (best_candidate %>% 
    filter(f1 == max(best_candidate$f1, na.rm = T)))$cutoff[1]

# # Accuracy
# pl.accuracy <-
#   ggplot(cutoffs, aes(x=cutoff, y = accuracy, group = facet), )+
#   geom_point(color = "darkgreen")+
#   geom_line(color = "darkgreen")+
#   labs(title = "Accuracy",
#        subtitle = "What overall share of texts is correctly classified?",
#        y = "Accuracy\n",
#        x = "Chosen semantic similarity cutoff")+
#   theme_bw()

# Balanced Accuracy
pl.baccuracy <-
  ggplot(data, aes(x=cutoff, y = baccuracy, group = facet), )+
  geom_point(color = "darkgreen")+
  geom_line(color = "darkgreen")+
  geom_vline(xintercept = best_candidate, linetype = "dotted") +
  labs(title = "<b>Balanced Accuracy</b>: What overall share of documents in each category is correctly classified?",
       y = "Accuracy\n",
       x = "")+
  theme_bw()+
  theme(plot.title = element_markdown())


# Precision and recall

pr <- data %>% 
  select(cutoff, precision, recall, facet) %>% 
  pivot_longer(cols = 2:3, names_to = "metric", values_to = "value")

pl.precrec <-
  ggplot(pr, aes(x=cutoff, y = value, color = metric))+
  geom_point()+
  geom_line()+
  geom_vline(xintercept = best_candidate, linetype = "dotted") +
  scale_color_manual(values = c("#d95f02", "#7570b3"))+
  labs(title = "<b>Precision & recall</b>",
       subtitle = "<span style = 'color:#d95f02;'><b>Precision</b></span>: What share of retrieved documents is actually relevant?<br><span style = 'color:#7570b3;'><b>Recall<b></span>: What share of actually relevant documents is is retrieved?",
       y = "Value\n",
       x = "",
       color = "")+
  theme_bw()+
  theme(legend.position = "none",
        plot.subtitle = element_markdown(),
        plot.title = element_markdown()) 

# F1 Score
pl.f1 <-
  ggplot(data, aes(x=cutoff, y = f1, group = facet), )+
  geom_point(color = "black")+
  geom_line(color = "black")+
  geom_vline(xintercept = best_candidate, linetype = "dotted") +
  labs(title = "<b>F1 Score</b>: Harmonized mean of recall & precision",
       y = "F1 score\n",
       x = paste("\nClassification cutoff applied to", scorename)) +
  theme_bw()+
  theme(plot.title = element_markdown()) 

if (!is.null(facetingvar)) {
  pl.f1 <- pl.f1 + facet_grid(. ~ facet)
  pl.precrec <- pl.precrec + facet_grid(. ~ facet)
  pl.baccuracy <- pl.baccuracy + facet_grid(. ~ facet)
  # pl.accuracy <- pl.accuracy + facet_grid(. ~ facet)
}

# Combined plot
pl.comb <- # pl.accuracy /
  pl.baccuracy / pl.precrec / pl.f1

ggsave(paste0("./output/plots/", plotname, ".png"), 
       pl.comb, width = 24, height = 27, units = "cm")

return(pl.comb)
}
```

One-option classifier
```{r}
cutoffs_definition <- calc_cutoff_candidates(cutoffvar = zeroshot_unfiltered$definition_zeroshot, targetvar = zeroshot_unfiltered$target)

plot_metrics(cutoffs_definition, 
             scorename = "Zeroshot Score with extended 'Digitality' definition",
             plotname = "Digital_classification_cutoff_zs_def")
```

note: positive = 1-negative

```{r}
cutoffs_binary <- calc_cutoff_candidates(cutoffvar = zeroshot_unfiltered$positive, targetvar = zeroshot_unfiltered$target)

plot_metrics(cutoffs_binary, 
             scorename = "Zeroshot Score with binary decision for/against Definition",
             plotname = "Digital_classification_cutoff_zs_bin")
```

```{r}
zeroshot_unfiltered %>% 
  ggplot(aes(x = definition_zeroshot, y = positive, colour = target)) +
  geom_point() +
  geom_smooth(method = "lm") +
  guides(colour = F) +
  facet_grid(vars(target)) +
  theme_minimal()
```

```{r}
cutoffs_nli <- calc_cutoff_candidates(cutoffvar = zeroshot_unfiltered$contradiction, targetvar = zeroshot_unfiltered$target)

plot_metrics(cutoffs_nli, 
             scorename = "Zeroshot Score with NLI hypothesis testing of definition contradiction",
             plotname = "Digital_classification_cutoff_nli_hypo_contradiction")
```

```{r}
zeroshot_unfiltered %>% 
  pivot_longer(cols = definition_zeroshot:contradiction,
               names_to = "label", 
               values_to = "score") %>% 
  ggplot() +
  geom_histogram(aes(x = score)) +
  facet_wrap(vars(label), ncol = 2) +
  scale_fill_manual(c("#619933", "#0380b5", "#9e3173")) +
  theme_minimal()
```

```{r}
classifications <- 
  zeroshot %>% 
  mutate(zs_digital = positive > negative,
         nli_digital = entailment > contradiction,
         nli_neutral = neutral > entailment & neutral > contradiction)
```


zeroshot with definition just thinks everything is rather digital:
```{r}
classifications %>% 
  count(target, zs_digital)
```


```{r}
classifications %>% 
  count(target, nli_digital)
```


```{r}
classifications %>% 
  count(target, nli_neutral, nli_digital)
```

multilabel zeroshot classification of subtopics

```{r}
bart_sub <- zeroshot %>% 
  mutate(max_subtopic = pmax(digital_communications, internet_technologies, digital_services_algorithms, digitized_data, na.rm = T)) %>%
  pivot_longer(c(digital_communications, internet_technologies, digital_services_algorithms, digitized_data, max_subtopic), 
               names_to = "label", 
               values_to = "score")

cutoffs_bart_sub <- calc_cutoff_candidates(cutoffvar = bart_sub$score, targetvar = bart_sub$target, facetingvar = bart_sub$label)

plot_metrics(data = cutoffs_bart_sub, 
             scorename = "Zeroshot Score with finegrained labels",
             plotname = "Digital_classification_cutoff_zs_sub",
             facetingvar = cutoffs_bart_sub$facet)
```
multilabel zeroshot classification of seed dictionary terms:

```{r}
bart_seed <- zeroshot %>% 
  mutate(max_seed = pmax(digital, algorithm, online, computer, internet, na.rm = T)) %>% 
  pivot_longer(c(digital, algorithm, online, computer, internet, max_seed), 
               names_to = "label", 
               values_to = "score")

cutoffs_bart_seed <- calc_cutoff_candidates(cutoffvar = bart_seed$score, targetvar = bart_seed$target, facetingvar = bart_seed$label)

plot_metrics(data = cutoffs_bart_seed, 
             scorename = "Zeroshot Score with finegrained labels",
             plotname = "Digital_classification_cutoff_zs_seed",
             facetingvar = cutoffs_bart_seed$facet)
```
```{r}
bart_sub <- zeroshot %>% 
  mutate(max_subtopic = pmax(digital_communications, internet_technologies, digital_services, digital_algorithms, digitized_data, digital_policy, na.rm = T)) %>%  #, mean_subtopic = (digital_communications + internet_technologies + digital_services + digital_algorithms + digitized_data + digital_policy) / 6)
  pivot_longer(c(digital_communications, internet_technologies, digital_services, digital_algorithms, digitized_data, digital_policy, max_subtopic), 
               names_to = "label", 
               values_to = "score")

cutoffs_bart_sub <- calc_cutoff_candidates(cutoffvar = bart_sub$score, targetvar = bart_sub$target, facetingvar = bart_sub$label)

plot_metrics(data = cutoffs_bart_sub, 
             scorename = "Zeroshot Score with finegrained labels",
             plotname = "Digital_classification_cutoff_zs",
             facetingvar = cutoffs_bart_sub$facet)
```
